Calculate all possible narrow band indices

### 2018-07-31 02_scripts/01_hyperspectral_indices/05_narrow-band-indices.Rmd
NBI -> NRI

```{r, results='hide'}
library(raster)
devtools::install_github("pat-s/hsdar")
library(hsdar)
library(pbmcapply)
library(glue)
library(magrittr)
library(purrr)
```

@@

```{r, cache=FALSE}
tmp <- pbmclapply(hyperspecs, function(x)  
  nbi_raster(x,
             filename = str_replace(glue("/data/patrick/mod/hyperspectral/",
                             "narrow-band-indices/narrow-band-indices-{name}",
                             name = basename(x@file@name)), ".tif", ".grd"), mc.cores = 15)) 
rm(tmp)
```

>>>>

```{r, results='hide'}
library(raster)
devtools::install_github("pat-s/hsdar")
library(hsdar)
library(pbmcapply)
library(glue)
library(magrittr)
library(purrr)
library(stringr)
```

@@

```{r, cache=FALSE}
tmp <- pbmclapply(hyperspecs, function(x)  
  nbi_raster(x,
             filename = str_replace(glue("/data/patrick/mod/hyperspectral/",
                             "narrow-band-indices/narrow-band-indices-{name}",
                             name = basename(x@file@name)), ".tif", ".grd"),
             bnames_prefix = "NRI"), mc.cores = 15)
rm(tmp)
```
